Import and process AODV3 Level2 AOD20 from Aeronet

### 2019-08-13 R/non_drake_code_and_md_files/03.2_AOD Variation.Rmd
organize folder

---
title: "AODV3 Level2 AOD2.0 from Aeronet Day Variation"
author: "Yang Liu"
date: "7/24/2019"
output:
  html_document:
    toc: true
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, message=FALSE, warning=FALSE,
                      error = F, fig.width = 8, fig.height = 4)
```

```{r}
source("~/liuyanguu/CWV/Code/cwv_funcs.R")
source(here::here("Code", "funcs_for_plots.R"))
#

@@

# aod_conus <- aod_conus[year(date)>2000]
aod_conus[,datetime:=date]
aod_conus[,date:=as.Date(date, "%Y-%m-%d")]
aod_conus[,dailyN:=.N, by = .(site, date)] # obs in a day by site,day
aod_conus <- aod_conus[dailyN>=20,]
summary(aod_conus[,.N,by = .(site, date)][,N])
aod_conus[,daysN:= uniqueN(date), by = site] # lasting days by site

@@

```{r,  fig.width=12, fig.height=5}
# summary1: aod1 calculates the mean and sd (SD) by day 
aod1 <- unique(aod_conus[,.(lat, lon, dailyN, daysN, month, season, 
                            mean_aod = mean(AOD_470nm), sd_aod = sd(AOD_470nm),
                            year = year(date)), by = .(site, date)])
# 290 sites: aod2 [290 * 6]
aod2 <- unique(aod1[,.(mediansd = median(sd_aod), Nobs = sum(dailyN),
                       yearmax = max(year), daysN, lon, lat),by = .(site)])[yearmax>=2018]

@@

```{r, fig.width=12, fig.height=5}
# print results with daysN > 500 
setorder(aod2, -mediansd)
rmarkdown::paged_table(aod2[daysN>1500])

plotAODscatter <- function(aod_data, bySeason = F){
  g1  <-  ggplot(data = aod_data[daysN>=500], aes(x = daysN, y = mediansd))+
      geom_point(size = 1, alpha = 1) + 
      theme_classic() + 
      ggrepel::geom_label_repel(data = aod_data[(daysN>1000&mediansd>0.013)|daysN>1500], aes(x = daysN, y = mediansd, label = site)) + 
      ggtitle("Median daily SD(AOD) vs. Total days by Station", subtitle = ("Stations with latest year >=2018")) + 
      labs(x = "Number of Observations", y = "Daily SD(AOD)")
  if(bySeason) {g1 <- g1 + facet_wrap(~season)}
  g1
}

plotAODmap <- function(aod_data, bySeason = F){
  g2 <- ggplot() +
          geom_polygon(data = map_data("state"), 
                       aes(x = long, y = lat, group = group), 
                       fill = 'NA', color = "grey") + 
          geom_point(data = aod_data[daysN>=500],
                     aes(x=lon, y=lat, color = mediansd, size = daysN),
                     alpha = 0.8) + 
          # coord_map("albers", parameters = list(at0 = 45.5, lat1 = 29.5), expand = T) + 
          scale_size_area(max_size = 12) + 
          scale_colour_viridis_c() + 
          labs(x = "Longitude", y = "Latitude", color= "Daily\nSD(AOD)", 
               size = "Number of\nDays") +
          ggrepel::geom_label_repel(data = aod_data[daysN>1000&mediansd>0.013], 
                                    aes(x = lon, y = lat, label = site)) + 
          theme_minimal() +
          ggtitle("SD by AERONET stations") +
          theme(legend.position ='right') 
  if(bySeason) g2 <- g2 + facet_wrap(~season)
  return(g2)
}
p1 <- plotAODscatter(aod2)
p2 <- plotAODmap(aod2)
gridExtra::grid.arrange(grobs = list(p1, p2), ncol = 2)

@@

### Calculating using past 3 years: 2016 - 2019

```{r}
# summary2: limiting the years! aod1 calculates the mean and sd (SD) by day 
aod1 <- unique(aod_conus[year>=2016,.(lat, lon, dailyN, daysN, month, season, 
                            mean_aod = mean(AOD_470nm), sd_aod = sd(AOD_470nm),
                            year = year(date)), by = .(site, date)])
# 290 sites: aod2 [290 * 6]
aod2 <- unique(aod1[,.(mediansd = median(sd_aod), Nobs = sum(dailyN),
                       yearmax = max(year), daysN, lon, lat),by = .(site)])[yearmax>=2018]

@@

```{r, fig.width=12, fig.height=5}
# print results with daysN > 500 
setorder(aod2, -mediansd)
rmarkdown::paged_table(aod2)
p1 <- plotAODscatter(aod2)
p2 <- plotAODmap(aod2)
gridExtra::grid.arrange(grobs = list(p1, p2), ncol = 2)
```

>>>>

---
title: "AODV3 Level2 AOD2.0 Aeronet: investigate within-day Variation"
author: "Yang Liu"
date: "7/24/2019"
output:
  html_document:
    toc: true
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, message=FALSE, warning=FALSE,
                      error = F, fig.width = 8, fig.height = 4)
```

```{r}
source("~/liuyanguu/CWV/Code/cwv_funcs.R")
source(here::here("Code", "funcs_for_plots.R"))

@@

# aod_conus <- aod_conus[year(date)>2000]
aod_conus[,datetime:=date]
aod_conus[,date:=as.Date(date, "%Y-%m-%d")]
aod_conus[,dailyN:=.N, by = .(site, date)] # obs in a day by site,day
aod_conus <- aod_conus[dailyN>=20,]
summary(aod_conus[,.N,by = .(site, date)][,N])

@@

```{r,  fig.width=12, fig.height=5}
# summary1: aod1 calculates the mean and sd (SD) by day 
aod1 <- unique(aod_conus[,.(lat, lon, dailyN, month, season, 
                            mean_aod = mean(AOD_470nm), sd_aod = sd(AOD_470nm),
                            year = year(date)), by = .(site, date)])
aod1[,daysN:= uniqueN(date), by = site] # lasting days by site 
# 290 sites: aod2 [290 * 6]
aod2 <- unique(aod1[,.(mediansd = median(sd_aod), Nobs = sum(dailyN),
                       yearmax = max(year), daysN, lon, lat),by = .(site)])[yearmax>=2018]

@@

```{r, fig.width=12, fig.height=5}
# print results with daysN > 500 
setorder(aod2, -mediansd)
rmarkdown::paged_table(aod2[daysN>1500])
library(ggrepel)
plotAODscatter <- function(aod_data, bySeason = F, daysN0 = 500){
  g1  <-  ggplot(data = aod_data[daysN>=daysN0], aes(x = daysN, y = mediansd))+
      geom_point(size = 1, alpha = 1) + 
      theme_classic() + 
      # ggrepel::geom_label_repel(data = aod_data[(daysN>daysN0*1.5 & mediansd> median(aod_data$mediansd))|daysN>daysN0*1.5], aes(x = daysN, y = mediansd, label = site)) + 
      ggtitle("Median daily SD(AOD) vs. Total days by Station", subtitle = ("Stations with latest year >=2018")) + 
      labs(x = "Number of Observations", y = "Daily SD(AOD)")
  if(bySeason) {g1 <- g1 + facet_wrap(~season)}
  g1
}

plotAODmap <- function(aod_data, bySeason = F, daysN0 = 500){
  g2 <- ggplot() +
          geom_polygon(data = map_data("state"), 
                       aes(x = long, y = lat, group = group), 
                       fill = 'NA', color = "grey") + 
          geom_point(data = aod_data[daysN >= daysN0],
                     aes(x=lon, y=lat, color = mediansd, size = daysN),
                     alpha = 0.8) + 
          # coord_map("albers", parameters = list(at0 = 45.5, lat1 = 29.5), expand = T) + 
          scale_size_area(max_size = 10) + 
          scale_colour_viridis_c() +
          labs(x = "Longitude", y = "Latitude", color= "Daily\nSD(AOD)", 
               size = "Number of\nDays") +
          # ggrepel::geom_text_repel(data = aod_data[daysN>daysN0*1.5 & mediansd>median(aod_data$mediansd)],
          #                           aes(x = lon, y = lat, label = site),
          #                           size =2.5, inherit.aes = F) +
          theme_minimal() +
          ggtitle("SD by AERONET stations") +
          theme(legend.position ='right') 
  if(bySeason) g2 <- g2 + facet_wrap(~season)
  return(g2)
}
plotAODmap(aod2,daysN0 = 300)
p1 <- plotAODscatter(aod2)
p2 <- plotAODmap(aod2)
gridExtra::grid.arrange(grobs = list(p1, p2), ncol = 2)

@@

### Calculating using past 3 years: 2015 - 2018

```{r}
# summary2: limiting the years! aod1 calculates the mean and sd (SD) by day 
aod1 <- unique(aod_conus[year>=2015,.(lat, lon, dailyN, month, season, 
                            mean_aod = mean(AOD_470nm), sd_aod = sd(AOD_470nm),
                            year = year(date)), by = .(site, date)])
# 290 sites: aod2 [290 * 6]
aod1[, daysN := uniqueN(date), by = site]
aod2 <- unique(aod1[,.(mediansd = median(sd_aod), Nobs = sum(dailyN),
                       yearmax = max(year), daysN, lon, lat),by = .(site)])[yearmax>=2018]

@@

## make and save plot

```{r, fig.width=12, fig.height=5}
# print results with daysN > 500 
setorder(aod2, -mediansd)
rmarkdown::paged_table(aod2)
p_aer <- plotAODmap(aod2, daysN0 = 300) + 
  ggtitle("Median Daily SD (AERONET AOD)", 
                   subtitle = "2015 - 2018")

# gridExtra::grid.arrange(grobs = list(p1, p_aer), ncol = 2)

D2 <- readRDS(here("Intermediate/DSCOVR_DailySD_AOD_bySite.rds"))
g_DS <- plotAODmap(D2, daysN0 = 5) + ggtitle("Median Daily SD (DSCOVR EPIC MAIAC AOD)", subtitle = "By AERONET Station, 2015 - 2018")

ggsave(p_aer, file = here("Figure","190731_DailySD_AER.png"),
      width = 6, height = 4)

ggsave(g_DS, file = here("Figure","190731_DailySD_DSCOVR.png"),
      width = 6, height = 4)

ggsave(grid.arrange(p_aer, g_DS, ncol = 2), file = here("Figure","190731_DailySD_DS_AERONET.png"),
      width = 12, height = 4)

### 2019-08-13 R/non_drake_code_and_md_files/03_import_AOD_V3.Rmd
organize folder

```{r}
source("~/liuyanguu/CWV/Code/cwv_funcs.R")
source("~/liuyanguu/AOD_CONUS/Code/funcs_for_plots.R")

@@

```{r, eval = T}
# https://aeronet.gsfc.nasa.gov/data_push/V3/AOD/AOD_Level20_All_Points_V3.tar.gz
# load aod data
# aod20_daily_dir <- "/data-coco/ECHO_PM/AeronetAODV3Level2/AOD/AOD20/DAILY/"
aod20_daily_dir <- "/data-coco/ECHO_PM/AeronetAODV3Level2/AOD/AOD20/ALL_POINTS/"
aod20_file_dir  <-  list.files(aod20_daily_dir, pattern = "*.lev20", full.names = TRUE)

# load site location file, only for limiting sites' locations to the US or to NEMIA
site_locations_2019 <- fread("/data-coco/ECHO_PM/AeronetAODV3Level2/AOD/AOD20/aeronet_locations_v3.txt")
aod_file_name <- gsub("^[0-9]{5,}_[0-9]{5,}_|\\.lev20", "", list.files(aod20_daily_dir, pattern = "*.lev20"))
aod_file_name[!aod_file_name%in%site_locations_2019$Site_Name]
# Among the 4 sites, Kitt-Peak_MP (Kitt Peak National Observatory) and UMBC_temp are in US.
setnames(site_locations_2019, c("Site_Name", "lon", "lat", "elev"))

@@

@@

```{r, eval = F}
# open one file and take a look at the data
t0 <- fread(aod20_file_dir[3])
t0[1,]

grep("Angstrom_Exponent", names(t0), value = T)
# read one file
vars_aod <- intersect(grep("AOD_", names(t0), value = T), grep("nm", names(t0), value = T))
# sort the wave lengths from low to high, and update the vars_aod
x_nm <- sort(readr::parse_number(vars_aod))
vars_aod <- paste0("AOD_", x_nm,"nm")
vars_wv <- paste0("Exact_Wavelengths_of_AOD(um)_", x_nm,"nm")
vars0 <- c("Date(dd:mm:yyyy)", "Time(hh:mm:ss)", "Day_of_Year","AERONET_Site_Name",
             "AERONET_Instrument_Number", 
             "Site_Latitude(Degrees)", 
             "Site_Longitude(Degrees)", 
             "Site_Elevation(m)", "Ozone(Dobson)", "NO2(Dobson)")
vars0_new <- c("date", "time", "dayofYear", "site",
                "instrumentNumber", "lat", "lon", 
                 "elev", "ozone", "NO2")
read.aod <- function(site_dir, vars_read, vars_newname){
  t1 <- fread(site_dir, select = vars_read, col.names = vars_newname)
  t1[, date := as.Date(date, format = "%d:%m:%Y")]
  t1[, hour := format(strptime(time, "%H:%M:%S"), "%H")]
  for (i in names(t1)) t1[get(i) == -999, (i):= NA] # set NA 
  t1
}

system.time(
file_list <- lapply(aod20_file_dir, read.aod, vars_read = c(vars0,vars_aod,vars_wv),  vars_newname = c(vars0_new,vars_aod,vars_wv)) # 440s
)
aod20_data_global <- rbindlist(file_list)

@@

vars_aod <- grep("AOD_", names(aod20_data_global), value = T)
vars_wv <- grep("Exact_Wavelengths_of_AOD", names(aod20_data_global), value = T)
# The 5 main wavelengths
aod_main <- c("AOD_340nm", "AOD_380nm", "AOD_440nm", "AOD_500nm", "AOD_675nm")
vars_aod_sub <- vars_aod[1:22]
aod_num <- readr::parse_number(vars_aod_sub)
# Drop the last two wavelengths because they are frequently off the main trend lines
aod20_data_global <- aod20_data_global[, -c("AOD_1020nm", "AOD_1640nm"), with = F]

@@

## Fit a poly(2) regression based on Kodi's code
# DT.m2 = melt(DT, measure = list(colA, colB), value.name = c("dob", "gender"))
# subset to aods and obs column and melt
# melt two groups of columns (AOD and Exact wavelength) in the same time: 
d <- melt(aod20_data_global[, c(vars_aod_sub,vars_wv[1:22], "obs"), with = F], measure = list(vars_aod_sub, vars_wv[1:22]),value.name = c("aod", "exact_wv"))
# choose non-NA and >0 AOD
d <- d[!is.na(aod)]
# d[, variable := readr::parse_number(levels(variable))[as.integer(variable)]]
# should have points on both sides, otherwise pick out the id
obs_os <- d[, by = obs, .(oneside = (max(exact_wv)-470)*(min(exact_wv)-470)>0)][oneside ==T, obs]
saveRDS(obs_os, "~/Intermediate/AOD_data/190621_obs_same_side")
length(obs_os)/aod20_data_global[,.N] # about 0.4% have points on one side of the 470 nm

@@

```{r, eval = F}
time0 <- Sys.time()
system.time(d2 <- d[, by = obs, .(AOD_470nm = exp(predict(lm(log(aod) ~  log(exact_wv) + I((log(exact_wv))^2)), newdata = data.frame(exact_wv = 470))))])
Sys.time() - time0 # 6.3 hours 6/19

@@

# If there are at least 4 non-NA, even on one side of the 470, I consider it fine,
# If there are 2 or 3 points, one side is not fine
# 1 points are set to NA, all of them are in obs_os as well, since there is only one point
length(obs_os) # 91911 
aod20_data_global[N_NAAOD <=4 & obs%in%obs_os,.N] # 91553, so most <=3 are on the same side of 470 nm anyway 
aod20_data_global[N_NAAOD ==3 & obs%in%obs_os,.N]

# because for those on the one side and requires long range extrapolating: need 5 or 6 points to be valid. For those with at least 5 points, most have close points within the allowed range: "AOD_440nm" "AOD_443nm" "AOD_490nm" "AOD_500nm"
allowed_range <- paste0("AOD_", aod_num[440<=aod_num & aod_num<=500],"nm")
aod20_data_global[obs%in%obs_os &is.na(AOD_440nm)&is.na(AOD_443nm)&is.na(AOD_490nm) &is.na(AOD_500nm), table(N_NAAOD)]
 # exterpolating with 5 or 6 might be fine 
 #    1     2     3     4     5     6 
 # 3332 37551   183    54     4     8 
aod20_data_pred470[N_NAAOD<=4 & obs%in%obs_os, AOD_470nm:=NA]
aod20_data_pred470 <- aod20_data_pred470[,.(date, time, hour, dayofYear, site, 
                                            lat, lon, N_NAAOD, AOD_470nm, AOD_440nm, AOD_500nm)]
date0 <- format(Sys.Date(), "%y%m%d")
# save results 
write.fst(aod20_data_pred470,          paste0("/data-coco/ECHO_PM/AeronetAODV3Level2/AOD_Level20_All_Points_V3_wPredAODat470nm_",date0, ".fst"), compress = 100)

@@

# create aod20_NEMIA_idLST, link Aeronet AOT to MAIAC grid (MCD19A2)

* created aod20_NEMIA_idLST that has AERONET Site_Name, idLSTpair0

@@

# Join AOT to MAIAC (MCD19A2)

* rolling join with nearest time (join_time) and by (idLSTpair0)

@@

# load lst data for 2018
read.lst <- function(sat = "terra", columns0 = NULL){
  if (sat != "terra") choose = "mcd19_T" else choose = "mcd19_A" # load terra by default
  lst_files <- list.files(path = "/data-coco/mcd19/fst/nemia/2018", pattern = choose, full.names = T)
  dt = rbindlist(lapply(lst_files, function(x)read.fst(x, as.data.table = T, columns  = columns0)))
  if(is.null(columns0)) dt[,c("x", "y", "inNEMIA"):=NULL]

  dt[, join_time:=overpass_time]
  setkey(dt, idLSTpair0, join_time)
  return(dt)
}
lst_terra <- read.lst()
print(object.size(lst_terra), unit = "GB") # 18 GB all the lst terra in 2018 (NEMIA, one year)
# make sure both are UTC time 
# attr(aod20_NEMIA_idLST$stn_time, "tzone")
# attr(lst_terra$overpass_time, "tzone")

@@

# time difference
aod_lst_terra[, diff_time_min:= as.numeric(overpass_time - stn_time)/60]
aod_lst_terra[, within30min_t:=0]
aod_lst_terra[abs(diff_time_min)<=30, within30min_t:=1]
table(aod_lst_terra$within30min_t)
# hist(aod_lst_terra[abs(diff_time_min)<=60, diff_time_min], 20)
hist(aod_lst_terra[within30min_t==1, diff_time_min])
mean(aod_lst_terra$within30min_t)

# vars0 <- c("overpass_index", "Optical_Depth_047", "AOD_Uncertainty", "Column_WV", "AOD_QA",  "RelAZ")
# vars_new <- paste0(vars0,"_t")
# setnames(aod_lst_terra, vars0, vars_new)
# set NA 
aod_lst_terra <- aod_lst_terra[within30min_t!=0,]

# Aqua  ~~~~ #### 
lst_aqua <- read.lst("aqua")
# rolling join
aod_lst_aqua <- aod20_NEMIA_idLST[lst_aqua, roll = 'nearest', nomatch = 0]
aod_lst_aqua[,.N]

>>>>

```{r}
source("~/liuyanguu/CWV/Code/cwv_funcs.R")
source("~/liuyanguu/AOD_CONUS/Code/funcs_for_plots.R")
```

@@

```{r, eval = T}
# https://aeronet.gsfc.nasa.gov/data_push/V3/AOD/AOD_Level20_All_Points_V3.tar.gz
# load aod data
aod20_file_dir  <-  list.files("/data-coco/ECHO_PM/AeronetAODV3Level2/AOD/AOD20/ALL_POINTS/", pattern = "*.lev20", full.names = TRUE)

# load site location file, only for limiting sites' locations to the US or to NEMIA
site_locations_2019 <- fread("/data-coco/ECHO_PM/AeronetAODV3Level2/AOD/AOD20/aeronet_locations_v3.txt")

aod_file_name <- gsub("^[0-9]{5,}_[0-9]{5,}_|\\.lev20", "", list.files(aod20_daily_dir, pattern = "*.lev20"))

aod_file_name[!aod_file_name%in%site_locations_2019$Site_Name]
# Among the 4 sites, Kitt-Peak_MP (Kitt Peak National Observatory) and UMBC_temp are in US.
setnames(site_locations_2019, c("Site_Name", "lon", "lat", "elev"))

@@

# aod_file_name[aod_file_name%in%site_list_NE]

@@

```{r, eval = F}
# open one file and take a look at the data
t0 <- fread(aod20_file_dir[1])
t0[1,]

grep("Angstrom_Exponent", names(t0), value = T)
# read one file
vars_aod <- intersect(grep("AOD_", names(t0), value = T), grep("nm", names(t0), value = T))
# sort the wave lengths from low to high, and update the vars_aod
x_nm <- sort(readr::parse_number(vars_aod))
vars_aod <- paste0("AOD_", x_nm,"nm")
vars_wv <- paste0("Exact_Wavelengths_of_AOD(um)_", x_nm,"nm")
vars0 <- c("Date(dd:mm:yyyy)", "Time(hh:mm:ss)", "Day_of_Year","AERONET_Site_Name",
             "AERONET_Instrument_Number", 
             "Site_Latitude(Degrees)", 
             "Site_Longitude(Degrees)", 
             "Site_Elevation(m)", "Ozone(Dobson)", "NO2(Dobson)")
vars0_new <- c("date", "time", "dayofYear", "site",
                "instrumentNumber", "lat", "lon", 
                 "elev", "ozone", "NO2")

read.aod <- function(site_dir, vars_read, vars_newname){
  t1 <- fread(site_dir, select = vars_read, col.names = vars_newname)
  t1[, date := as.Date(date, format = "%d:%m:%Y")]
  t1[, hour := format(strptime(time, "%H:%M:%S"), "%H")]
  for (i in names(t1)) t1[get(i) == -999, (i):= NA] # set NA 
  t1
}
system.time(
file_list <- lapply(aod20_file_dir, read.aod, vars_read = c(vars0,vars_aod,vars_wv),  vars_newname = c(vars0_new,vars_aod,vars_wv)) # 440s
)
aod20_data_global <- rbindlist(file_list)

@@

# The 5 main wavelengths
# aod_main <- c("AOD_340nm", "AOD_380nm", "AOD_440nm", "AOD_500nm", "AOD_675nm")
vars_wv <- grep("Exact_Wavelengths_of_AOD", names(aod20_data_global), value = T)
vars_aod <- grep("AOD_", names(aod20_data_global), value = T)
vars_aod_sub <- vars_aod[1:22]
# aod_num <- readr::parse_number(vars_aod_sub)
# Drop the last two wavelengths because they are frequently off the main trend lines
aod20_data_global <- aod20_data_global[, -c("AOD_1020nm", "AOD_1640nm"), with = F]

@@

## Fit a poly(2) regression based on Kodi's code
# DT.m2 = melt(DT, measure = list(colA, colB), value.name = c("dob", "gender"))
# subset to aods and obs column and melt
# melt two groups of columns (AOD and Exact wavelength) in the same time: 
d <- melt(aod20_data_global[, c(vars_aod_sub,vars_wv[1:22], "obs"), with = F], measure = list(vars_aod_sub, vars_wv[1:22]),value.name = c("aod", "exact_wv"))
# choose non-NA and >0 AOD
d <- d[!is.na(aod)]
# d[, variable := readr::parse_number(levels(variable))[as.integer(variable)]]
# should have points on both sides, otherwise pick out the id
obs_os <- d[, by = obs, .(oneside = (max(exact_wv)-0.47)*(min(exact_wv)-0.47)>0)][oneside ==T, obs]
saveRDS(obs_os, "~/Intermediate/AOD_data/190621_obs_same_side")
length(obs_os)/aod20_data_global[,.N] # about 0.4% have points on one side of the 470 nm

@@

```{r, eval = F}
time0 <- Sys.time()
system.time(d2 <- d[, by = obs, .(AOD_470nm = exp(predict(lm(log(aod) ~  log(exact_wv) + I((log(exact_wv))^2)), newdata = data.frame(exact_wv = 0.47))))])
Sys.time() - time0 # 6.3 hours 6/19 for the world.

@@

# If there are at least 4 non-NA, even on one side of the 470, I consider it fine,
# If there are 2 or 3 points, one side is not fine
# If there is only 1 point, set to NA, all of them are in obs_os anyway, since there is only one point
length(obs_os) # 91911

# because for those on the one side and requires long range extrapolating: need 5 or 6 points to be valid. For those with at least 5 points, most have close points within the allowed range: "AOD_440nm" "AOD_443nm" "AOD_490nm" "AOD_500nm"

 # exterpolating with 4, 5 or 6 might be fine 
 #    1     2     3     4     5     6 
 # 3332 37551   183    54     4     8 
aod20_data_pred470[N_NAAOD<=4 & obs%in%obs_os, AOD_470nm:=NA]
aod20_data_pred470 <- aod20_data_pred470[,.(date, time, hour, dayofYear, site, 
                           lat, lon, N_NAAOD, AOD_470nm, AOD_440nm, AOD_500nm)]
date0 <- format(Sys.Date(), "%y%m%d")
# save results 
write.fst(aod20_data_pred470,          paste0("/data-coco/ECHO_PM/AeronetAODV3Level2/AOD_Level20_All_Points_V3_wPredAODat470nm_",date0, ".fst"), compress = 100)

@@

# Rolling join AOT to MAIAC (MCD19A2)

1. created aod20_NEMIA_idLST that has AERONET Site_Name matched with idLSTpair0

@@

2. rolling join with nearest time (join_time) and by (idLSTpair0)

@@

read_lst <- function(sat = "terra"){
  lst_files <- list.files(path = "/data-coco/mcd19/fst/nemia/2018", pattern = "mcd19_T", full.names = T)
  if (sat != "terra") choose = "mcd19_A" else choose = "mcd19_T" # load terra by default
  lst_files <- list.files(path = "/data-coco/mcd19/fst/nemia/2018", pattern = choose, full.names = T)
  dt = rbindlist(lapply(lst_files, function(x)read.fst(x, as.data.table = T)))
  dt[, join_time:=overpass_time]
  setkey(dt, idLSTpair0, join_time)
  return(dt)
}
lst_terra <- read_lst()
# 18 GB all the lst terra in 2018 (NEMIA, one year)
print(object.size(lst_terra), unit = "GB") 
# make sure both are UTC time 
attr(aod20_NEMIA_idLST$stn_time, "tzone")
attr(lst_terra$overpass_time, "tzone")

@@

# time difference
aod_lst_terra[, diff_time_min:= as.numeric(overpass_time - stn_time)/60]
aod_lst_terra[, within30min_t:=0]
aod_lst_terra[abs(diff_time_min)<=30, within30min_t:=1]
table(aod_lst_terra$within30min_t)
# hist(aod_lst_terra[abs(diff_time_min)<=60, diff_time_min], 20)
hist(aod_lst_terra[within30min_t==1, diff_time_min])
mean(aod_lst_terra$within30min_t)
aod_lst_terra <- aod_lst_terra[within30min_t!=0,]

# Aqua  ~~~~ #### 
lst_aqua <- read_lst("aqua")
# rolling join
aod_lst_aqua <- aod20_NEMIA_idLST[lst_aqua, roll = 'nearest', nomatch = 0]
aod_lst_aqua[,.N]
